Identity Blockchain - Proof of Identity

### 2022-07-09 paper.tex
circom Nin owns Kid

\lstset{
	language=circom,
	backgroundcolor=\color{verylightblue},
	extendedchars=true,
	basicstyle=\footnotesize\ttfamily,
	showstringspaces=false,
	showspaces=false,
	numbers=left,
	numberstyle=\footnotesize,
	numbersep=9pt,
	tabsize=2,
	breaklines=true,
	showtabs=false,
	captionpos=b
}

@@

\hfill\begin{minipage}{\dimexpr\textwidth-20px}
\begin{lstlisting}[language=circom]
pragma circom 2.0.0;

template NinOwnsKid(){
	//TODO: What happens to uint256 when converted to signal

@@

	//private:

>>>>

\lstset{
	language=circom,
	backgroundcolor=\color{lightgray},
	extendedchars=true,
	basicstyle=\footnotesize\ttfamily,
	showstringspaces=false,
	showspaces=false,
	numbers=left,
	numberstyle=\footnotesize,
	numbersep=9pt,
	tabsize=2,
	breaklines=true,
	showtabs=false,
	captionpos=b
}

@@

\hfill\begin{minipage}{\dimexpr\textwidth-20px}
Using https://github.com/zkp-application/circom-rsa-verify for now, MIT license.
Which probably doesn't work, we should check (sha256?).
The next line is used on a file of shape:
-----BEGIN PUBLIC KEY-----
...
-----END PUBLIC KEY-----
-----BEGIN CERTIFICATE-----
...
-----END CERTIFICATE-----
We assume: 
	modulus = Subject Modulus
	exp = Subject Exponent

openssl x509 -in Identification.pem -text -noout

\begin{lstlisting}[language=circom]
pragma circom 2.0.0;

include "./utils/rsa_verify.circom"
include "./circomlib/circuits/sha256/sha256.circom"
include "./circomlib/bitify.circom"

//hashNumberOfWords = 4 for sha256
//rsaNumberOfWords = 32 for 2048 rsa
//we use words of 64 bits
template NinOwnsKid(
		rsaNumberOfWords, 
		hashNumberOfWords, 
		lengthInBitsOfSignedMessage,
		lengthOfNinInBits
){
	//TODO: What happens to uint256 when converted to signal

@@

	//private:
	signal input Nin;
	//Kid, CA signature
	singal input exp[rsaNumberOfWords];
	signal input sign[rsaNumberOfWords];
	signal input modulus[rsaNumberOfWords];

	//we need some inputs to verify what is signed
	//and that Nin in the right place in the signed message
  signal input messageToBeSigned[lengthInBitsOfSignedMessage];
	signal input Nin[lengthOfNinInBits];

	//TODO: Insert Nin into messageToBeSigned in the right place
	//or create constraint on the corresponding bits

	component sha = Sha256(lengthInBitsOfSignedMessage);
	for (int i = 0; i<lengthInBitsOfSignedMessage; i++) {
		sha.in[i] <== messageToBeSigned[i]
	}

	var hashed[hashNumberOfWords];//4x64 bit
	var hashedBits[hashNumberOfWords*64];
	for (int i=0; i<hashNumberOfWords*64;i++){
		hashedBits[i] <== sha.out[i];
	}
	component b2n = Bits2Num(64);
	//TODO:Can we use a component multiple times?
	//Will all the constraints be generated
	for (int i=0;i<hashNumberOfWords;i++){
		for (int j=0;j<64;j++){
			b2n.in[j] <== hashedBits[i*64+j];
		}
	  hashed[i] <== b2n.out;
	}

	//lets assume sha256WithRSAEncryption

	component rsa = RsaVerifyPkcs1v15(64, rsaNumberOfWords, 17, 4);
	for (var i = 0; i < rsaNumberOfWords; i++){
		rsa.exp[i] <== exp[i];
		rsa.sign[i] <== sign[i];
		rsa.modulus[i] <== modulus[i];
	}
	for (var i = 0; i<hashNumberOfWords; i++){
		rsa.hashed[i] <== hashed[i];
	}

	//Check CA on CA approved list
	//On blockchain mapping (uint256 => bool) public CAValid
